Wrangle transcripts

### 2023-09-29 code/data_prep.Rmd
start data prep and analyses

@@

# Transcript wrangle - new
```{r}

real_offset <- real_offset %>% filter(gameConfig=="game41")
wrangle_transcript <- function(game_num){
read_csv(here("data/clean_transcripts", str_c(game_num,".csv")), show_col_types=F) |> 
  select(start, end, text, speaker, trial, role, echo, description, backchannel) |> 
    fill(trial) %>% 
  mutate(start=start/1000, end=end/1000) |> 
    nest(data=c(start, end, text, speaker, trial, role, echo, description, backchannel))
}

@@

```{r}
timed_transcripts <-  transcripts |>
  mutate(start=start-offset_sec, end=end-offset_sec) |> 
  select(-offset_sec, -gameId) |> 
  mutate(trialNumStart=NA, trialNumEnd=NA) |> 
  rename(game=gameConfig) |> 
  bind_rows(stage_timing) |> 
  group_by(game) |> 
  arrange(start) |> 
  fill(trialNumStart) |> 
  arrange(end) |> 
  fill(trialNumEnd, .direction="up") |> 
  arrange(game) |> 
  filter(!is.na(text)) |> 
  write_csv(here("data/timed_transcript.csv"))
```

```{r}
# Quick check

timed_transcripts %>% filter(!is.na(trialNumStart)) %>%

@@

```{r}
# how many trial mismatches are there?
timed_transcripts |> filter(end>0) |> filter(!is.na(trialNumEnd)) |> #it's in the game region, not rules or post game
 mutate(mismatch=trialNumEnd-trialNumStart) |> 
  group_by(mismatch) |> 
  tally()

#so like a third mismatch, and only a couple off by more than 1
```

>>>>

label_image <- function(string){
  new_string <- case_when(
    string=="/experiment/B1.jpg" ~ "walk",
    string=="/experiment/D1.jpg" ~ "swim",
    string=="/experiment/E1.jpg" ~ "jump",
    string=="/experiment/I1.jpg" ~ "hold",
    string=="/experiment/banana.png"~ "banana",
    string=="/experiment/bird.jpeg" ~ "bird",
    string=="/experiment/dog.png" ~ "dog",
    string =="/experiment/apple.png" ~ "apple"
  )
  return(new_string)
}

less_raw_data <- raw_data %>% select(game, target, distractor, trialNum, targetNum, repNum, response, correct, time, listener=playerId, speaker) %>% 
  mutate(across(c(target, distractor, response), ~ label_image(.x))) %>% write_csv(here("data/clean_data.csv"))
```

@@

# Transcript wrangle - new

wrangle_transcript <- function(game_num){
 read_csv(here("data/clean_transcripts", str_c(game_num,".csv")), show_col_types=F) |> 
  select(start, end, text, speaker, trial, role, echo, description, backchannel) |> 
    fill(trial) %>% 
  mutate(start=start/1000, end=end/1000) |> 
    nest(data=c(start, end, text, speaker, trial, role, echo, description, backchannel))
}

@@

```{r}
timed_transcripts <-  transcripts |>
  mutate(start=start-offset_sec, end=end-offset_sec) |> 
  select(-offset_sec, -gameId) |> 
  mutate(trialNumStart=NA, trialNumEnd=NA) |> 
  rename(game=gameConfig) |> 
  bind_rows(stage_timing) |> 
  group_by(game) |> 
  arrange(start) |> 
  fill(trialNumStart) |> 
  arrange(end) |> 
  fill(trialNumEnd, .direction="up") |> 
  arrange(game) |> 
  filter(!is.na(text))

echoes <- timed_transcripts %>% select(game,trial, echo) %>% filter(echo=="Y") %>% unique()

trial_timing <- stage_timing %>% select(game, trial=trialNumStart, trial_start=start)

transcript_full <- timed_transcripts %>% select(-echo, -exclude) %>% left_join(echoes) %>% 
  left_join(trial_timing) %>% 
  rename(start_time=start, end_time=end) %>% 
  write_csv(here("data/timed_transcript.csv"))
```

# Checks
```{r}
# Quick check -- for kid talking, so auto-trial and hand-trial align?

transcript_full %>% filter(!is.na(trialNumStart)) %>% filter(str_detect(speaker, "id")) %>% filter(!is.na(role)) %>% filter(trial!=trialNumStart)

# we'll go with the by-hand method -- these mostly seem to be when there's a wide span of time! possibly due to whisper being silly or us hand filling due to whisper missing things

@@
